Flexibility of interactions depends on habitat suitability

### 2019-08-30 paper/manuscript.Rmd
Correct minor error reporting standard deviations

The group level variation among communities was larger than that among species.
The standard deviation (in the parameters scale) of the community intercepts was `r round(sd_loc_id$Estimate, 2)` [`r round(random_cor$Q2.5, 2)`, `r round(sd_loc_id$Q97.5, 2)`] while the standard deviation of the species intercept was `r round(sd_org_id$Estimate, 2)` [`r round(sd_org_id$Q2.5, 2)`, `r round(sd_org_id$Q97.5, 2)`], and that of the species' suitability slope was `r round(sd_org_id_suitability$Estimate, 2)` [`r round(sd_org_id_suitability$Q2.5, 2)`, `r round(sd_org_id_suitability$Q97.5, 2)`] (95% credible intervals shown within square brakets). 
Interestingly, the slope the relationship between suitability and normalised degree was negatively correlated with the species' intercept in the model (Figure \@ref(fig:fig-random-effects)b). 
The mean correlation coefficient was `r round(random_cor$Estimate, 2)` [`r round(random_cor$Q2.5, 2)`, `r round(random_cor$Q97.5, 2)`].

>>>>

The group level variation among communities was larger than that among species.
The standard deviation (in the parameters scale) of the community intercepts was `r round(sd_loc_id$Estimate, 2)` [`r round(sd_loc_id$Q2.5, 2)`, `r round(sd_loc_id$Q97.5, 2)`] while the standard deviation of the species intercept was `r round(sd_org_id$Estimate, 2)` [`r round(sd_org_id$Q2.5, 2)`, `r round(sd_org_id$Q97.5, 2)`], and that of the species' suitability slope was `r round(sd_org_id_suitability$Estimate, 2)` [`r round(sd_org_id_suitability$Q2.5, 2)`, `r round(sd_org_id_suitability$Q97.5, 2)`] (95% credible intervals shown within square brakets). 
Interestingly, the slope the relationship between suitability and normalised degree was negatively correlated with the species' intercept in the model (Figure \@ref(fig:fig-random-effects)b). 
The mean correlation coefficient was `r round(random_cor$Estimate, 2)` [`r round(random_cor$Q2.5, 2)`, `r round(random_cor$Q97.5, 2)`].
